Juliacon Proceedings in Quarto

### 2023-11-15 template.qmd

---
title: Juliacon Proceedings in Quarto
format:
  juliacon-proceedings-pdf:
    keep-tex: true  
  juliacon-proceedings-html: default
author:
  - name: Patrick Altmeyer
    affiliations:
      - Delft University of Technology
    orcid: 0000-0003-4726-8613
    email: p.altmeyer@tudelft.nl
    url: https://www.paltmeyer.com/
abstract: |
  This document is a Quarto template demonstrating the `juliacon-proceedings` format.
year: 2023
keywords: [Template, Demo, Quarto, JuliaCon]
bibliography: bibliography.bib  
---

@@

```{julia}
#| lst-label: lst-1
#| lst-cap: A listing caption
#| eval: false
#| echo: true

@@

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
```

>>>>

---
title: Juliacon Proceedings in Quarto
format:
  juliacon-proceedings-pdf:
    keep-tex: true  
  juliacon-proceedings-html: default
author:
  - name: Patrick Altmeyer
    affiliations:
      - Delft University of Technology
    orcid: 0000-0003-4726-8613
    email: p.altmeyer@tudelft.nl
    url: https://www.paltmeyer.com/
abstract: |
  This document is a template demonstrating the `juliacon-proceedings` format. It is a standard Quarto document composed of Markdown, LaTeX and code chunks. It is rendered to PDF and HTML. The PDF is rendered using the `juliacon-proceedings-pdf` format, which is based on the `juliacon-proceedings` LaTeX class. The HTML is rendered using the `juliacon-proceedings-html` format, which is based on the `juliacon-proceedings` HTML template.
keywords: [Template, Demo, Quarto, JuliaCon]
bibliography: bibliography.bib  
jupyter: julia-1.9
---

```{julia}
#| echo: false
#| output: false

using Pkg; Pkg.activate(".")
```

@@

```{julia}
#| lst-label: lst-1
#| lst-cap: A listing caption
#| echo: true

@@

x = -3.0:0.01:3.0
y = rand(length(x));
```
